\newpage
\section{Education \& Public Outreach}

Education and Public Outreach has several repositories for documentation during Rubin Observatory Construction. 1.) EPO maintains a collection of documents in Docushare, and has been attentive to using this as the repository for documents as they are moved from a "working" to a "final" state. The EPO Docushare collection includes evaluation reports, needs assessment reports, presentations, progress reports, and strategy and design documents. 2.) EPO uses Confluence as a collaborative workspace to create, share and discuss files, ideas, meeting minutes, specifications, mockups, diagrams, and projects. The EPO Confluence file structure is updated regularly, and pages that are no longer active have been archived. In some cases, Confluence pages contain links to external sources, (e.g., Google Suite).  3.) EPO maintains a collection of working documents in Google Suite; this material is of a similar type to that found in Confluence, and also includes content being developed for Rubin Observatory's public-facing website in Operations, and will eventually be moved to that website's content management system. 4.) Individual EPO team members use Dropbox for design and visual documents. In cases where files require persistence and/or access by the EPO team, they are moved to Docushare. 5.) Finally, the EPO technical team uses GitHub to develop software, and contains technological notes regarding the construction of online EPO products and tools.

Links to EPO specific documents can be found here:

\begin{itemize}

	\item {\bf Docushare:}  \url{https://docushare.lsst.org/docushare/dsweb/View/Collection-21}
	\item {\bf Confluence:} \href{https://confluence.lsstcorp.org/pages/viewpage.action?pageId=25690606}{Education and Public Outreach (EPO)}
	\item {\bf Google Suite:}  \url{https://drive.google.com/drive/u/0/folders/1psuXwgM5EsnM-2h58Dj14sfTTZD1kpo7}
	\item {\bf Github:} \url{https://github.com/lsst-epo}
	
\end{itemize}

